---
title: "Integrating In-house Data with Datasets in CompassDB"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{integrat_inhouse_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CompassR)
```

Load the in-house data, expression is a data frame with gene as rownames and sample as column names (by AverageExpression of Seurat), linkage is a data frame output from the Linkage of Signac package.
```{r}
gene = "EMP2"
tissue = "Pancreas"

lexpr_df = read.csv("http://compass-db.com/static/test_data/lung_expr_df.csv", header = TRUE, row.names = 1)
llink_df = read.csv("http://compass-db.com/static/test_data/lung_linkage_bed.csv", header = TRUE, row.names = 1)
```

Query the expression and linkage data from the CompassDB.
```{r}
expr_vec = query_exprssion("hg38", gene)
link_res = query_linkage("hg38", gene)

link_df = link_res[["linkage"]]
sample_df = link_res[["samples"]]

sample_df = sample_df[sample_df$bio_source == tissue, ]
sample_df = sample_df[, c("sample_id", "bio_source")]
colnames(sample_df) = c("Sample", "Group")
sample_df = sample_df[order(sample_df$Group), ]
link_df = link_df[link_df$sample %in% sample_df$Sample, 1:(ncol(link_df)-5)]
expr_df = data.frame(t(expr_vec)[sample_df$Sample, ])
colnames(expr_df) = c("Gene")
expr_df$Sample = rownames(expr_df)
```

Merge the in-house data with the CompassDB data.
```{r}
colnames(llink_df) = colnames(link_df)
link_df = rbind(link_df, llink_df)
link_df = link_df[link_df$gene == gene, ]

sample_df = rbind(sample_df, data.frame(Sample = colnames(lexpr_df), Group = "Lung", row.names = colnames(lexpr_df)))
expr_df = rbind(expr_df, data.frame(Gene = unlist(lexpr_df[gene, ]), Sample = colnames(lexpr_df), row.names =  colnames(lexpr_df)))
```


Visualize the linkage and expression information from both in-house data and CompassDB.
```{r}
link_df$sample_id = link_df$sample
genome_track_map(link_df, sample_df, gene, expr_df, assembly = "hg38", legend.position="left", t = -20, b = 20)
```

Find the peaks that are highly correlated with the EMP2 expression in Lung tissue.
```{r}
track_plot = plot_genome_track(link_df, gene, "hg38", sample_df$Sample)
peaks = track_plot[[length(track_plot)]]
peaks$name = as.character(peaks$name)
peak_order = make_peak_group(link_df, peaks, sample_df)

ht_peak_order = peak_order[peak_order[, "Lung"] >0.5 & peak_order[, "Pancreas"]<0.5, ]
print(dim(ht_peak_order))
ht_peaks = rownames(ht_peak_order)

### TFBS analysis
peak_vec = sub(":", "-", as.character(peaks))
ht_peaks = peak_vec[as.numeric(ht_peaks)]
tf = tf_binding("hg38", paste0(ht_peaks, collapse = "_"))
p = plot_giggle(tf)
p
```





