---
title: "Analysis in a single sample"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sample_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We explored the regulation of the CD79B gene in a single peripheral blood mononuclear cell (PBMC) sample. CD79B is crucial for forming the B-cell receptor complex and is expressed almost exclusively on B cells.

```{r setup}
library(CompassR)
library(Seurat)
library(Signac)
### Adjust the timeout to 10 minutes due to file size
options(timeout=600)
```
Load the Seurat object and update the path to the fragments file online.
```{r}
### Sample level analysis
obj = readRDS(url("https://g-297ec7.1d0d8d.03c0.data.globus.org/seurat_object/GSM5065525_GSM5065524.rds", "rb"))
DefaultAssay(obj) = "ATAC"
frag = Fragments(obj)[[1]]
frag = UpdatePath(frag, new.path = "https://g-297ec7.1d0d8d.03c0.data.globus.org/fragments/GSM5065525_GSM5065524.tsv.gz", verbose = TRUE)
obj@assays$ATAC@fragments[[1]] = frag
```

Get the coverage plot for the gene of interest.
```{r}
gene = "CD79B"
p = CoveragePlot(
  object = obj,
  group.by = "annot.primary",
  region = gene,
  features = gene,
  annotation = TRUE,
  peaks = TRUE,
  extend.upstream = 10000,
  extend.downstream = 10000
)
print(p)
```

Extract the links for the gene of interest and plot the TF binding sites.
```{r}
link_df_obj = Links(obj)
gene_link = link_df_obj[link_df_obj$gene == "CD79B"]

peak_vec = sub(":", "-", gene_link$peak)
peak_vec

tf = tf_binding("hg38", paste0(peak_vec, collapse = "_"))
p = plot_giggle(tf)
print(p)
```
